### 2021-12-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@e77d6c40b71a34d1032e8b719339193704d2bd58 🚀

Binary classifiers are usually assessed by measuring properties of their
confusion matrix, \emph{i.e.} the contingency table reporting true/false
positive/negative hits. The same approach is used to evaluate
\emph{e.g.} species occurrence models (Allouche et al., 2006). A
confusion matrix is laid out as

@@

list of problems to solve - baseline values and response to bias -
effect of training set bias on performance - which models need the least
amount of interactions to work

summary of the results

@@

>>>>

Binary classifiers are usually assessed by measuring properties of their
confusion matrix, \emph{i.e.} the contingency table reporting true/false
positive/negative hits. A confusion matrix is laid out as

@@

The same approach is used to evaluate \emph{e.g.} species distribution
models (SDMs). Indeed, the training and evaluation of SDMs as binary
classifiers suffers from the same issue of low prevalence. In a previous
work, Allouche et al. (2006) suggested that \(\kappa\) was a better test
of model performance than the True Skill Statistic (TSS), which we will
refer to as Youden's informedness (or \(J\)); these conclusions were
later criticized by Somodi et al. (2017), who emphasized that
informedness' relationship to prevalence depends on assumptions about
bias in the model. Although this work offers recommendations about the
comparison of models, it doesn't establishes baselines or good practices
for training on imbalanced ecological data. Within the context of
networks, there are three specific issues that need to be adressed.
First, what values of performance measures are we expecting for a
classifier that has poor performance? This is particularly important as
it can evaluate whether low prevalence can lull us into a false sense of
predictive accuracy. Second, independently of the question of model
evaluation, is low prevalence an issue for \emph{training}, and can we
remedy it? Finally, because the low amount of data on interaction makes
a lot of imbalance correction methods (see \emph{e.g.} Branco et al.,
2015) hard to apply, which indicators can be optimized with the least
amount of positive interaction data?

We establish that due to the low prevalence of interactions, even poor
classifiers applied to food web data will reach a high accuracy; this is
because the measure is dominated by the accidental correct predictions
of negatives. The \(F_1\) score and positive predictive values are less
sensitive to bias, but \textbf{TODO}

Chicco et al. (2021) - MCC maximizes other measures, other measures do
not maximize MCC, except notably when prevalence is low, or the baseline
guessing level is uncertain, which applies to networks. In this cases,
informedness should be used as a maximization criterion.

@@

\leavevmode\hypertarget{ref-Branco2015SurPre}{}%
Branco, P., Torgo, L., \& Ribeiro, R. (2015, May 13). \emph{A Survey of
Predictive Modelling under Imbalanced Distributions}.
\url{http://arxiv.org/abs/1505.01658}

\leavevmode\hypertarget{ref-Chicco2021MatCor}{}%
Chicco, D., Tötsch, N., \& Jurman, G. (2021). The Matthews correlation
coefficient (MCC) is more reliable than balanced accuracy, bookmaker
informedness, and markedness in two-class confusion matrix evaluation.
\emph{BioData Mining}, \emph{14}, 13.
\url{https://doi.org/10.1186/s13040-021-00244-z}

\leavevmode\hypertarget{ref-Somodi2017PreDep}{}%
Somodi, I., Lepesi, N., \& Botta‐Dukát, Z. (2017). Prevalence dependence
in model goodness measures with special emphasis on true skill
statistics. \emph{Ecology and Evolution}, \emph{7}(3), 863--872.
\url{https://doi.org/10.1002/ece3.2654}
